基于卷积神经网络的视觉目标跟踪算法研究

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/Chap_IGCF.tex
删除重复参考文献

\textbf{网络结构} 表 \ref{tab:InstMask} 和图 \ref{fig:IGCF_net} 中展示了 InstMask 的网络结构。InstMask 的主干是基于 ResNet50 \cite{He2016DeepRL} 构建的，它由一个主干块和三个残差块组成。
InstMask 的输入是一个尺寸为 160$\times$160$\times$3 的图像补丁。它被发送到主干块，生成尺寸为 40$\times$40$\times$64 的特征图。然后将特征图依次送入 3 个残差块，分别生成大小为 40$\times$40$\times$256，20$\times$20$\times$512，10$\times$10$\times$1024 的特征图。随后，将获得的特征图送入三个卷积层以生成长度为 3136 的向量，该向量具有全局感受野，能够感知有关目标的所有上下文信息。最后，将此向量尺寸调整为 56$\times$56，以获得最终的分割模板。InstMask 是一个轻量级的网络，配备有 InstMask 的 IGCF 跟踪器可以在具有 Intel E5-2620 CPU 内核的平台上以 5 FPS 运行，能够较好地平衡跟踪准确性和速度，使跟踪器在包括自动驾驶、机器人技术和增强现实等实际应用中进行部署成为可能。

>>>>

\textbf{网络结构} 表 \ref{tab:InstMask} 和图 \ref{fig:IGCF_net} 中展示了 InstMask 的网络结构。InstMask 的主干是基于 ResNet50 \cite{he2016deep} 构建的，它由一个主干块和三个残差块组成。
InstMask 的输入是一个尺寸为 160$\times$160$\times$3 的图像补丁。它被发送到主干块，生成尺寸为 40$\times$40$\times$64 的特征图。然后将特征图依次送入 3 个残差块，分别生成大小为 40$\times$40$\times$256，20$\times$20$\times$512，10$\times$10$\times$1024 的特征图。随后，将获得的特征图送入三个卷积层以生成长度为 3136 的向量，该向量具有全局感受野，能够感知有关目标的所有上下文信息。最后，将此向量尺寸调整为 56$\times$56，以获得最终的分割模板。InstMask 是一个轻量级的网络，配备有 InstMask 的 IGCF 跟踪器可以在具有 Intel E5-2620 CPU 内核的平台上以 5 FPS 运行，能够较好地平衡跟踪准确性和速度，使跟踪器在包括自动驾驶、机器人技术和增强现实等实际应用中进行部署成为可能。

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/Chap_MTP.tex
删除重复参考文献

注意公式 \ref{equ:dcf} 和公式 \ref{equ:siamese} 之间存在相似之处，主要区别在于进行相关计算的核：DCF 的核是在线学习的 $w_{\theta}$ ，而孪生网络的核是 $\phi_\theta(\textbf z)$。为了使孪生网络具有模型自适应能力，我们需要使用当前视频的第一帧标注信息来自适应调整 $\phi_\theta(\textbf z)$。调整 $\phi_\theta(\textbf z)$ 有两种设计选择：更改 $\phi_\theta(\cdot)$ 或更改 $\textbf z$。但是，更改 $\phi_\theta(\cdot)$ 可能会导致繁琐的元学习设置，难以确保离线训练的嵌入空间 \cite{ROAM, DBLP:conf/aaai/JungYNCH20} 的特征表示能力。相反，我们的解决方案是以简单的方式通过更改 $\textbf z$ 来执行孪生跟踪器的模型自适应，即在第一帧使用目标真实标注信息仅在几次梯度下降迭代中修改模板像素。与当前的孪生跟踪模型自适应方法相比，该方法具有以下优点：

>>>>

注意公式 \ref{equ:dcf} 和公式 \ref{equ:siamese} 之间存在相似之处，主要区别在于进行相关计算的核：DCF 的核是在线学习的 $w_{\theta}$ ，而孪生网络的核是 $\phi_\theta(\textbf z)$。为了使孪生网络具有模型自适应能力，我们需要使用当前视频的第一帧标注信息来自适应调整 $\phi_\theta(\textbf z)$。调整 $\phi_\theta(\textbf z)$ 有两种设计选择：更改 $\phi_\theta(\cdot)$ 或更改 $\textbf z$。但是，更改 $\phi_\theta(\cdot)$ 可能会导致繁琐的元学习设置，难以确保离线训练的嵌入空间 \cite{ROAM, MetaRTT} 的特征表示能力。相反，我们的解决方案是以简单的方式通过更改 $\textbf z$ 来执行孪生跟踪器的模型自适应，即在第一帧使用目标真实标注信息仅在几次梯度下降迭代中修改模板像素。与当前的孪生跟踪模型自适应方法相比，该方法具有以下优点：

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/Chap_end.tex
删除重复参考文献

实际上，视频具有关于目标的丰富信息，并且这种时间信息是视频理解和跟踪的重要基础。
例如，在视频目标检测中，FGFA~\cite{zhu2017flow} 在特征级别上利用了时间一致性。该算法通过沿运动路径聚合相邻帧的特征来改善每帧特征，从而提高了视频识别精度。
在视频目标分割中，STCNN~\cite{xu2019spatiotemporal} 引入了时间模块，该模块着重于捕获动态表观和运动线索以提供目标分割的指导信息。
在基于判别性相关滤波器的目标跟踪中，FlowTrack~\cite{zhu2018end} 专注于利用连续帧中丰富的流信息来改善特征表示和跟踪精度。
但是，如何在孪生跟踪器中利用时间信息尚未得到广泛研究。

@@

% key words: temporal modeling, model the temporal information, temporal fusion, inter-frame information, improve the feature representation, temporal aggregation, poor object appearance
在本章中，我们旨在充分利用孪生跟踪器中的时间信息。
%(We introduce a novel siamese tracking architecture equipped with a temporal aggregation module to make full use of inter-frame information.)
%(In this work, to deal with the issues raised above, we propose a novel tracker to aggregate features of adjacent frames by ...)
%(In this paper, we develop an end-to-end temporal aggregation module in siamese architecture to utilize both the power of siamese trackers and the inter-frame information.)
我们提出了一种新型孪生跟踪架构，配备有时间聚合模块，该模块通过聚合相邻帧中的特征来改善每帧中目标的特征表示。
这种时间聚合策略使孪生跟踪器可以处理由于运动模糊等原因导致的目标表观信息退化现象。
为实现聚合时间信息的目的，我们在孪生网络的特征提取网络中沿时间维度 \cite{lin2019tsm} 移动通道特征。
请注意，由于视频中目标的运动 \cite{zhu2017flow}，相邻帧中同一目标的特征通常不会在空间上对齐，因此仅对残差层 \cite{lin2019tsm} 进行时间平移，以保证孪生跟踪器的特征学习能力。
与其他时间融合方法 \cite{tao2016siamese, gladh2016deep} 不同，本章采用的方法能够在大规模数据集上进行端到端训练。此外，本章采用的时间融合方法易于实现，而无需更改孪生跟踪架构或使用光流 \cite{zhu2018end} 信息。

@@

\section{相关工作}
\subsection{时间信息在视频动作识别中的应用}
远程时间结构在理解动作视频的动态过程中起着重要的作用。但是，主流的卷积神经网络框架通常集中在表观信息和短期运动上，因此缺乏整合远程时间结构的能力。最近，有一些尝试 \cite{Motionlets} 来解决这个问题。这些方法主要依赖于具有预定采样间隔的密集时间采样。当将这种方法应用于长视频序列时，将导致过高的计算成本，这限制了其在现实世界中的应用，并存在丢失长视频中重要信息的风险。因此，在 文献 \cite{TSN} 中，Wang 等人基于远程时间结构建模的思想，提出了一种视频动作识别的新型框架。该框架结合了稀疏的时间采样策略和视频级别的监督，可以使用整个动作视频进行高效学习。该框架采用稀疏采样方案在长视频序列上提取短视频片段，其中采样点沿时间维度均匀分布。在此基础上，采用分层结构聚合来自采样视频段的信息。因此，该算法能够对整个视频的远程时间结构进行建模。此外，这种稀疏的采样策略可以使用较低的成本保存视频信息，从而可以在合理的时间和计算资源预算下，在长视频序列上进行端到端学习。% Temporal Segment Networks: Towards Good Practices for Deep Action Recognition 1608
在文献 \cite{TRN} 中，Zhou 等人认为时间关系推理使人类能够根据过去情况分析当前情况，并就下一步可能发生的情况提出假设。时间关系推理对于视频动作识别至关重要，它构成了描述事件的基础。因此，作者提出了一种有效且可解释的网络模块，即时间关系网络（temporal relational reasoning，TRN），该模块旨在学习和推理多个时间尺度上视频帧之间的时间依赖性。% Temporal Relational Reasoning in Videos 1711
在文献 \cite{AdaFuse} 中，Meng 等人认为时间建模是有效的视频动作识别的关键。虽然了解时间信息可以提高动态动作的识别精度，但是消除时间冗余和重用过去的特征可以大大节省计算量，从而实现有效的动作识别。因此，作者提出了一种称为 AdaFuse 的自适应时间融合网络，该网络可以动态融合当前和过去特征图中的通道，以实现强大的时间建模，从而提高识别精度和效率。% ADAFUSE: ADAPTIVE TEMPORAL FUSION NETWORK FOR EFFICIENT ACTION RECOGNITION
\subsection{时间信息在视频目标检测中的应用}
在视频目标检测算法 TCNN \cite{TCNN} 中，Kang 等人认为在相邻帧中目标的位置和表观应保持连续性，即，预测的边界框位置和检测置信度不应在短时间内发生剧烈变化。然而，如果将图像目标检测框架直接应用于视频目标检测任务中，则目标的检测置信度往往会在相邻帧之间发生显著变化。为了解决这一问题，作者提出了一个深度学习框架，该框架扩展了流行的图像检测框架 R-CNN \cite{girshick2014rich} 和 Faster R-CNN \cite{ren2015faster}，通过合并相邻帧的时间信息和上下文信息来解决视频中的通用目标检测问题。该算法可以在相邻帧中传播检测结果，并可沿着跟踪算法生成的轨迹修改检测置信度，从而有效地提高现有图像检测框架在视频目标检测任务中的性能。% T-CNN: Tubelets with Convolutional Neural Networks for Object Detection from Videos 1604
该工作虽然提高了识别准确性，但是具有较高的计算成本。为了减少计算量，在文献 \cite{DeepFeature} 中，Zhu 等人基于深度特征流提出了一种快速、准确的视频目标检测方法。该方法在稀疏的关键帧上应用图像检测网络，通过流场将深度特征图从关键帧传播到其他帧。传播后的特征类似于原始特征。通常，流估计和特征传播比卷积特征的计算快得多。因此，该方法避免了计算瓶颈，显著提高了检测速度。当流场也由网络估算时，整个架构将进行端到端训练，可同时优化目标检测任务和流网络。% Deep Feature Flow for Video Recognition
\subsection{时间信息在视觉目标跟踪中的应用}
大多数现有的相关滤波跟踪器仅考虑当前帧的表观特征，几乎无法从运动和帧间信息中受益。在诸如部分遮挡和形变之类的挑战中，缺少时间信息会降低跟踪性能。目标跟踪所处理的是视频信息，因此时序信息很重要。
%以前有很多工作利用时序信息进行目标跟踪。
在文献 \cite{DeepMotion} 中，Gladh 等人首次提出将表观信息与深度运动特征融合以进行视觉跟踪。表观特征仅对单帧中的静态信息进行编码，而深度运动特征则对基于光流的多帧信息进行整合。因此，运动特征可以捕获与表观特征互补的场景动态特征。因此，作者研究了深度运动特征对视觉目标跟踪的影响，并提出将表观特征与深度运动特征进行融合，以进行视觉目标跟踪。
该方法虽然利用光流提高了视觉目标跟踪算法的性能，但采用的是在动作识别任务中预训练的深层光流网络，并没有在视觉目标跟踪任务中进行端到端训练，因此没有获得最佳跟踪效果。
为了解决这一问题，FlowTrack \cite{FlowTrack} 首次提出在深度学习框架中共同训练光流网络和跟踪网络，从而利用连续帧中丰富的光流信息进一步提高特征表示和跟踪精度。首先，作者将包括光流估计、特征提取、特征聚合和相关滤波器跟踪在内的各个组件制定为网络中的特殊层。然后，按照光流的引导，以指定的时间间隔对历史特征图进行扭曲并与当前特征图进行聚合，从而捕获视频中的时间信息。

>>>>

实际上，视频具有关于目标的丰富信息，并且这种时间信息是视频理解和跟踪的重要基础。
例如，在视频目标检测中，FGFA~\cite{zhu2017flow} 在特征级别上利用了时间一致性。该算法通过沿运动路径聚合相邻帧的特征来改善每帧特征，从而提高了视频识别精度。
在视频目标分割中，STCNN~\cite{xu2019spatiotemporal} 引入了时间模块，该模块着重于捕获动态表观和运动线索以提供目标分割的指导信息。
在基于判别性相关滤波器的目标跟踪中，FlowTrack~\cite{FlowTrack} 专注于利用连续帧中丰富的流信息来改善特征表示和跟踪精度。
但是，如何在孪生跟踪器中利用时间信息尚未得到广泛研究。

@@

% key words: temporal modeling, model the temporal information, temporal fusion, inter-frame information, improve the feature representation, temporal aggregation, poor object appearance
在本章中，我们旨在充分利用孪生跟踪器中的时间信息。
%(We introduce a novel siamese tracking architecture equipped with a temporal aggregation module to make full use of inter-frame information.)
%(In this work, to deal with the issues raised above, we propose a novel tracker to aggregate features of adjacent frames by ...)
%(In this paper, we develop an end-to-end temporal aggregation module in siamese architecture to utilize both the power of siamese trackers and the inter-frame information.)
我们提出了一种新型孪生跟踪架构，配备有时间聚合模块，该模块通过聚合相邻帧中的特征来改善每帧中目标的特征表示。
这种时间聚合策略使孪生跟踪器可以处理由于运动模糊等原因导致的目标表观信息退化现象。
为实现聚合时间信息的目的，我们在孪生网络的特征提取网络中沿时间维度 \cite{lin2019tsm} 移动通道特征。
请注意，由于视频中目标的运动 \cite{zhu2017flow}，相邻帧中同一目标的特征通常不会在空间上对齐，因此仅对残差层 \cite{lin2019tsm} 进行时间平移，以保证孪生跟踪器的特征学习能力。
与其他时间融合方法 \cite{tao2016siamese, gladh2016deep} 不同，本章采用的方法能够在大规模数据集上进行端到端训练。此外，本章采用的时间融合方法易于实现，而无需更改孪生跟踪架构或使用光流 \cite{FlowTrack} 信息。

@@

\section{相关工作}
\subsection{时间信息在视频动作识别中的应用}
远程时间结构在理解动作视频的动态过程中起着重要的作用。但是，主流的卷积神经网络框架通常集中在表观信息和短期运动上，因此缺乏整合远程时间结构的能力。最近，有一些尝试 \cite{Motionlets} 来解决这个问题。这些方法主要依赖于具有预定采样间隔的密集时间采样。当将这种方法应用于长视频序列时，将导致过高的计算成本，这限制了其在现实世界中的应用，并存在丢失长视频中重要信息的风险。因此，在 文献 \cite{TSN} 中，Wang 等人基于远程时间结构建模的思想，提出了一种视频动作识别的新型框架。该框架结合了稀疏的时间采样策略和视频级别的监督，可以使用整个动作视频进行高效学习。该框架采用稀疏采样方案在长视频序列上提取短视频片段，其中采样点沿时间维度均匀分布。在此基础上，采用分层结构聚合来自采样视频段的信息。因此，该算法能够对整个视频的远程时间结构进行建模。此外，这种稀疏的采样策略可以使用较低的成本保存视频信息，从而可以在合理的时间和计算资源预算下，在长视频序列上进行端到端学习。% Temporal Segment Networks: Towards Good Practices for Deep Action Recognition 1608
在文献 \cite{TRN} 中，Zhou 等人认为时间关系推理使人类能够根据过去情况分析当前情况，并就下一步可能发生的情况提出假设。时间关系推理对于视频动作识别至关重要，它构成了描述事件的基础。因此，作者提出了一种有效且可解释的网络模块，即时间关系网络（temporal relational reasoning，TRN），该模块旨在学习和推理多个时间尺度上视频帧之间的时间依赖性。% Temporal Relational Reasoning in Videos 1711
在文献 \cite{AdaFuse} 中，Meng 等人认为时间建模是有效的视频动作识别的关键。虽然了解时间信息可以提高动态动作的识别精度，但是消除时间冗余和重用过去的特征可以大大节省计算量，从而实现有效的动作识别。因此，作者提出了一种称为 AdaFuse 的自适应时间融合网络，该网络可以动态融合当前和过去特征图中的通道，以实现强大的时间建模，从而提高识别精度和效率。% ADAFUSE: ADAPTIVE TEMPORAL FUSION NETWORK FOR EFFICIENT ACTION RECOGNITION
\subsection{时间信息在视频目标检测中的应用}
在视频目标检测算法 TCNN \cite{TCNN} 中，Kang 等人认为在相邻帧中目标的位置和表观应保持连续性，即，预测的边界框位置和检测置信度不应在短时间内发生剧烈变化。然而，如果将图像目标检测框架直接应用于视频目标检测任务中，则目标的检测置信度往往会在相邻帧之间发生显著变化。为了解决这一问题，作者提出了一个深度学习框架，该框架扩展了流行的图像检测框架 R-CNN \cite{girshick2014rich} 和 Faster R-CNN \cite{ren2015faster}，通过合并相邻帧的时间信息和上下文信息来解决视频中的通用目标检测问题。该算法可以在相邻帧中传播检测结果，并可沿着跟踪算法生成的轨迹修改检测置信度，从而有效地提高现有图像检测框架在视频目标检测任务中的性能。% T-CNN: Tubelets with Convolutional Neural Networks for Object Detection from Videos 1604
该工作虽然提高了识别准确性，但是具有较高的计算成本。为了减少计算量，在文献 \cite{DeepFeature} 中，Zhu 等人基于深度特征流提出了一种快速、准确的视频目标检测方法。该方法在稀疏的关键帧上应用图像检测网络，通过流场将深度特征图从关键帧传播到其他帧。传播后的特征类似于原始特征。通常，流估计和特征传播比卷积特征的计算快得多。因此，该方法避免了计算瓶颈，显著提高了检测速度。当流场也由网络估算时，整个架构将进行端到端训练，可同时优化目标检测任务和流网络。% Deep Feature Flow for Video Recognition
\subsection{时间信息在视觉目标跟踪中的应用}
大多数现有的相关滤波跟踪器仅考虑当前帧的表观特征，几乎无法从运动和帧间信息中受益。在诸如部分遮挡和形变之类的挑战中，缺少时间信息会降低跟踪性能。目标跟踪所处理的是视频信息，因此时序信息很重要。
%以前有很多工作利用时序信息进行目标跟踪。
在文献 \cite{gladh2016deep} 中，Gladh 等人首次提出将表观信息与深度运动特征融合以进行视觉跟踪。表观特征仅对单帧中的静态信息进行编码，而深度运动特征则对基于光流的多帧信息进行整合。因此，运动特征可以捕获与表观特征互补的场景动态特征。因此，作者研究了深度运动特征对视觉目标跟踪的影响，并提出将表观特征与深度运动特征进行融合，以进行视觉目标跟踪。
该方法虽然利用光流提高了视觉目标跟踪算法的性能，但采用的是在动作识别任务中预训练的深层光流网络，并没有在视觉目标跟踪任务中进行端到端训练，因此没有获得最佳跟踪效果。
为了解决这一问题，FlowTrack \cite{FlowTrack} 首次提出在深度学习框架中共同训练光流网络和跟踪网络，从而利用连续帧中丰富的光流信息进一步提高特征表示和跟踪精度。首先，作者将包括光流估计、特征提取、特征聚合和相关滤波器跟踪在内的各个组件制定为网络中的特殊层。然后，按照光流的引导，以指定的时间间隔对历史特征图进行扭曲并与当前特征图进行聚合，从而捕获视频中的时间信息。

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/english/Chap_MTP_english.tex
删除重复参考文献

Note that Equ. (\ref{equ:dcf}) and Equ. (\ref{equ:siamese}) bear some similarities with each other, and the main difference lies in the kernel term for correlation: the kernel of DCF is the online-learned $w_{\theta}$, and the kernel of the Siamese network is $\phi_\theta(z)$. In order for the Siamese network to have the model adaptation ability, we need to adapt $\phi_\theta(z)$ using the first frame ground truth annotation of the current video. There are two design choices to adapt $\phi_\theta(z)$: changing $\phi_\theta(\cdot)$ or changing $z$. However, changing $\phi_\theta(\cdot)$ may cause too much tedious meta-learning settings to ensure the generative ability of offline-trained embedding space \cite{ROAM, DBLP:conf/aaai/JungYNCH20}. In contrast, our solution is in a simple way to perform model adaptation of Siamese trackers by changing $z$, i.e., modifying template pixels in only a few gradient-descent iterations using the target ground-truth at the first frame. Compared with current model adaptation methods of Siamese trackers, the proposed method has the following advantages. First, we never modify parameters of the Siamese network to preserve the representation ability of offline-trained embedding space. Second, different from current template update methods \cite{zhu2018distractor, Zhang_2019_ICCV}, which aim to combine the target features from previous frames, we focus on the initial adaptation using target ground-truth at the first frame. Finally, our model adaptation method is pluggable, in the sense that it does not alter the overall architecture of the base tracker. In the next subsection, we will show how the popular adversarial example generation methods can be used to perform template pixel manipulation for model adaptation.

>>>>

Note that Equ. (\ref{equ:dcf}) and Equ. (\ref{equ:siamese}) bear some similarities with each other, and the main difference lies in the kernel term for correlation: the kernel of DCF is the online-learned $w_{\theta}$, and the kernel of the Siamese network is $\phi_\theta(z)$. In order for the Siamese network to have the model adaptation ability, we need to adapt $\phi_\theta(z)$ using the first frame ground truth annotation of the current video. There are two design choices to adapt $\phi_\theta(z)$: changing $\phi_\theta(\cdot)$ or changing $z$. However, changing $\phi_\theta(\cdot)$ may cause too much tedious meta-learning settings to ensure the generative ability of offline-trained embedding space \cite{ROAM, MetaRTT}. In contrast, our solution is in a simple way to perform model adaptation of Siamese trackers by changing $z$, i.e., modifying template pixels in only a few gradient-descent iterations using the target ground-truth at the first frame. Compared with current model adaptation methods of Siamese trackers, the proposed method has the following advantages. First, we never modify parameters of the Siamese network to preserve the representation ability of offline-trained embedding space. Second, different from current template update methods \cite{zhu2018distractor, Zhang_2019_ICCV}, which aim to combine the target features from previous frames, we focus on the initial adaptation using target ground-truth at the first frame. Finally, our model adaptation method is pluggable, in the sense that it does not alter the overall architecture of the base tracker. In the next subsection, we will show how the popular adversarial example generation methods can be used to perform template pixel manipulation for model adaptation.

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/english/Chap_end_english.tex
删除重复参考文献

Actually, the video has rich information about the target and such temporal information is an important basis for video understanding and tracking.
For example, in video object detection, FGFA \cite{zhu2017flow} leverages temporal coherence on feature level. It improves the per-frame features by aggregation of nearby features along the motion paths, and thus improves the video recognition accuracy.
In video object segmentation, STCNN \cite{xu2019spatiotemporal} introduces a temporal coherence module, which focuses on capturing the dynamic appearance and motion cues to provide the guidance of object segmentation.
In discriminative correlation filter-based object tracking, FlowTrack \cite{zhu2018end} focuses on making use of the rich flow information in consecutive frames to improve the feature representation and the tracking accuracy. 
However, how to utilize the temporal information in siamese trackers has not been widely studied yet.

@@

% key words: temporal modeling, model the temporal information, temporal fusion, inter-frame information, improve the feature representation, temporal aggregation, poor object appearance
In this paper, we aim to take full advantage of temporal information in siamese trackers.
%(We introduce a novel siamese tracking architecture equipped with a temporal aggregation module to make full use of inter-frame information.)
%(In this work, to deal with the issues raised above, we propose a novel tracker to aggregate features of adjacent frames by ...)
%(In this paper, we develop an end-to-end temporal aggregation module in siamese architecture to utilize both the power of siamese trackers and the inter-frame information.)
We introduce a novel siamese tracking architecture equipped with a temporal aggregation module, which improves the per-frame features by aggregating features from adjacent frames.
This temporal fusion strategy enables the siamese tracker to handle poor object appearance like motion blur, occlusion, \textit{etc}.
To achieve this, we shift the channels along the temporal dimension \cite{lin2019tsm} in the backbone of the siamese network.
Note that features of the same object are usually not spatially aligned across frames due to video motion \cite{zhu2017flow}, so the temporal shift is only performed on the residual layers \cite{lin2019tsm} to preserve the spatial feature learning capability of the siamese tracker.
Different from other temporal fusion methods \cite{tao2016siamese, gladh2016deep}, the proposed method is able to be trained end-to-end on large-scale datasets.
%The proposed temporal aggregation module is trained end-to-end in the siamese network.
%(This module enables our module to be trained end-to-end on large-scale datasets.)
Additionally, our temporal fusion method is easy to implement, without changing the siamese tracking architecture or using optical flow \cite{zhu2018end}.

>>>>

Actually, the video has rich information about the target and such temporal information is an important basis for video understanding and tracking.
For example, in video object detection, FGFA \cite{zhu2017flow} leverages temporal coherence on feature level. It improves the per-frame features by aggregation of nearby features along the motion paths, and thus improves the video recognition accuracy.
In video object segmentation, STCNN \cite{xu2019spatiotemporal} introduces a temporal coherence module, which focuses on capturing the dynamic appearance and motion cues to provide the guidance of object segmentation.
In discriminative correlation filter-based object tracking, FlowTrack \cite{FlowTrack} focuses on making use of the rich flow information in consecutive frames to improve the feature representation and the tracking accuracy. 
However, how to utilize the temporal information in siamese trackers has not been widely studied yet.

@@

% key words: temporal modeling, model the temporal information, temporal fusion, inter-frame information, improve the feature representation, temporal aggregation, poor object appearance
In this paper, we aim to take full advantage of temporal information in siamese trackers.
%(We introduce a novel siamese tracking architecture equipped with a temporal aggregation module to make full use of inter-frame information.)
%(In this work, to deal with the issues raised above, we propose a novel tracker to aggregate features of adjacent frames by ...)
%(In this paper, we develop an end-to-end temporal aggregation module in siamese architecture to utilize both the power of siamese trackers and the inter-frame information.)
We introduce a novel siamese tracking architecture equipped with a temporal aggregation module, which improves the per-frame features by aggregating features from adjacent frames.
This temporal fusion strategy enables the siamese tracker to handle poor object appearance like motion blur, occlusion, \textit{etc}.
To achieve this, we shift the channels along the temporal dimension \cite{lin2019tsm} in the backbone of the siamese network.
Note that features of the same object are usually not spatially aligned across frames due to video motion \cite{zhu2017flow}, so the temporal shift is only performed on the residual layers \cite{lin2019tsm} to preserve the spatial feature learning capability of the siamese tracker.
Different from other temporal fusion methods \cite{tao2016siamese, gladh2016deep}, the proposed method is able to be trained end-to-end on large-scale datasets.
%The proposed temporal aggregation module is trained end-to-end in the siamese network.
%(This module enables our module to be trained end-to-end on large-scale datasets.)
Additionally, our temporal fusion method is easy to implement, without changing the siamese tracking architecture or using optical flow \cite{FlowTrack}.
